### 2021-03-11 paper.Rmd
add sage frames and caption

> figure 14

>>>>

\begin{figure}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-001.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-016.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-038.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-074.png}

}
\caption{Selected frames from using a grand tour of mouse retina single cell RNA-seq data with the radial transformation described in @Laa2020-uv. Here the sage display was used to identify and verify cluster sepearation between the three highlighted clusters estimated from a clustering algorithm.}\label{fig:mouse-cluster}
\end{figure}
